Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Visuals
Work in progress.
Updated Box-Plot
Work in progress.
Updated Experiments
Improved experiment description.

            \begin{figure}
                \centering
                \includegraphics[width=0.65\textwidth]{img/fig_elite_projection.pdf}
                \caption{Projection of the historically Elite solutions towards the Champion.} \label{fig.elite_projection}
                \end{figure}

@@

            The goal of our fist experiment was to have fun, while improving the graphics with best images.

>>>>

            \begin{figure}
                \centering
                \includegraphics[width=0.65\textwidth]{img/fig_elite_projection.pdf}
                \caption{Projection of an Elite solution (found on the right) towards the Champion (at the left).} \label{fig.elite_projection}
                \end{figure}

@@

            The goal of the first experiment was to confirm that this paper’s
            proposed strategy obtained improved results over our basic
            technique, which created a new population with a random generation
            of a new set of candidate solutions. We chose Ackley as the first
            Classic Benchmark Function for Optimization to test our algorithm
            behavior, where Figure~\ref{fig.fun_ackley} shows its corresponding
            Box and Whisker chart, and we summarized the results in
            Table~\ref{tab.fun_ackley5} and Table~\ref{tab.fun_ackley10} (for
            five and ten dimensions, respectively).
